WordRec Experiment

### 2019-03-15 Data_and_analysis/revisons1_pilot.Rmd
revisions

exp1 <- read_delim("exp1_rev2_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

@@

Fit the aggregate  data 
```{r}
data_s <- sound_all_exp1 %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

@@

```
Optimal model
```{r}
#Extract cefficieny

@@

Here fit the same models for every subject
```{r}

@@

Unimodal conditions
```{r}
## Generate model predictions to plot with human data in the unimodal conditions

@@

ggplot(sounds_exp1, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_s, aes(x=distance, y=prediction), col='black')+
  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
  geom_line(data=pred_nl_s, aes(x=distance, y=prediction), col='red')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)

ggplot(concepts_exp1, 
       aes(x = distance, y = mean)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_c, aes(x=distance, y=prediction), col='black')+
  #geom_line(data=uni_me_s, aes(x=distance, y=prediction), col='blue')+
  geom_line(data=pred_nl_c, aes(x=distance, y=prediction), col='red')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(. ~ ID)

Here compute the optimal combination
```{r}

@@

ggplot(data_preds, 
       aes(x = pred, y = Joint)) +
           #col = factor(concept_dist), 
          # shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) + 
  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(ID ~ model)+
  theme_few()+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=0.5, y=0.95, size=2, fontface = "bold", col="red")+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

@@

>>>>

exp1 <- read_delim("data_rev_real1.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

@@

Fit the aggregate  data,

This a replcition of the unimodal data with aggregated data
```{r}
data_s <- sound_all_exp1 %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

@@

```
Optimal model

This is a replication of the optimality analysis for aggregated data

```{r}
#Extract cefficieny

@@

Here fit a different model for every subject
There are probably convergence issues with some participants, should check this later
(I think I should take those out of the analysis)
```{r}

@@

How to plot this? (but this visualization is not crucial)
Plot for every condition? or just change color for every participant (maybe too much to parse)
PLot just the means and ci?

```{r}
## Generate model predictions to plot with human data in the unimodal conditions

@@

ggplot(sounds_exp1, 
       aes(x = distance, y = mean, group = distance)) + 
  geom_boxplot()+
  #geom_line()+
  #geom_smooth()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_smooth(data=pred_s, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) #+ facet_grid(. ~ ID)

ggplot(subset(concepts_exp1, ID=="subject_1"), 
       aes(x = distance, y = mean, col = ID)) + 
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
  #                position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=subset(pred_c,ID=="subject_1"), aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) #+ facet_grid(. ~ ID)

```
Here compute the cue combination analysis for each participant
```{r}

@@

@@

Plot by subject, not sure how to do it 
```{r}
ggplot(data_preds, 
       aes(x = pred, y = Joint)) +
           #col = factor(concept_dist), 
          # shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) + 
  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(ID ~ model)+
  theme_few()+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=0.5, y=0.95, size=2, fontface = "bold", col="red")+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

```{r}
#Make hitogram of optimality

histo_all <- correlations %>%
  group_by(ID) %>%
  filter(cor == max(cor)) %>%
  arrange(ID, model, cor)

histo_norm <- correlations %>%
  filter(model != 'Descriptive') %>%
  group_by(ID) %>%
  filter(cor == max(cor)) %>%
  arrange(ID, model, cor)

ggplot(histo_all, 
      aes(x = model)) +
  stat_count(width = 0.5)+
  #geom_histogram()+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +#  facet_grid(Segmentation ~ language)+
  #scale_y_continuous(labels = scales::percent)+
  xlab("Model") +ylab("Count")

ggplot(histo_norm, 
      aes(x = model)) +
  stat_count(width = 0.5)+
  #geom_histogram()+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +#  facet_grid(Segmentation ~ language)+
  #scale_y_continuous(labels = scales::percent)+
  xlab("Model") +ylab("Count")

```
Here I calculate the reliance on visual vs. auditory

```{r}

weight <- data_models %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b)

weight_sum <- weight %>% 
  mutate(temp = 'temp') %>%
  group_by(temp) %>%
  multi_boot_standard(col = "prop")

weight_separate <- weight %>%
  select(ID, weight_u, weight_b) %>%
  gather (key, value, weight_u, weight_b)

weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)

weight.ci=boot.ci(weight.boot, 
                  conf = 0.95,
                  type = c('perc'))

#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]

weight.median <- weight.ci$t0
weight.median_low <- weight.ci$percent[4]
weight.median_up <- weight.ci$percent[5]

ggplot(data=weight, aes(x=prop, y=..count..)) +
  geom_histogram(alpha=0.5, binwidth = 0.4)+
  geom_vline(xintercept = weight.median, col='red')+
  geom_vline(xintercept = weight.median_low, linetype='dashed') +
  geom_vline(xintercept = weight.median_up, linetype='dashed') +
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) +
  coord_cartesian(xlim=c(0.01,100))

```
I should do a test whether the variance is due to measurement noise or to geniune between-subject variability 
I should do the writing to see how these things will be intgrated
Here do the modality preference test (the same analysis I did for the aggragated data)

HERE
Old indivudual analysis used in version 1 of the submitteed paper
```{r echo=FALSE, warning = FALSE}

##Here we fit logistic regression to each participant
##The logitic regression is equivalent to the descriptive model without the bias term
##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant

joint_bysub_1 <- joint_all_exp1 %>%
  group_by(ID) %>%
  do(fit_joint_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

joint_bysub_2 <- joint_all_exp2 %>%
  group_by(ID) %>%
  do(fit_joint_2 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

joint_bysub_3 <- joint_all_exp3 %>%
  group_by(ID) %>%
  do(fit_joint_3 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

##Extract auitory and visual variances for each participant

#Exp1
bimodal_bysub_1 = tidy(joint_bysub_1, fit_joint_1) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var)

#Exp2
bimodal_bysub_2 = tidy(joint_bysub_2, fit_joint_2) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var)

#Exp3
bimodal_bysub_3 = tidy(joint_bysub_3, fit_joint_3) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var)

```{r echo=FALSE}
#number of participants relying exlusiviely on one modality
#cut off: a factor of 10

#participants who rely on both modalities 
bimodal_bysub_good_1 <- bimodal_bysub_1 %>%
  filter(bimod > 0.1) %>%
  filter(bimod < 10)

#participants who rely only on the visual modality
#(this includes participants who relied  only on the visual modality but gave noisy responses, leading to negative values of the variance, probably due to mistaking "same" for "different", or vice versa)
only_visual_N_1 <- bimodal_bysub_1 %>%
  filter(abs(bimod) < 0.1) %>%
  nrow()

#participants who rely only on the auditory modality

only_sound_N_1 <- bimodal_bysub_1 %>%
  filter(abs(bimod) > 10) %>%
  nrow()

#participants who relied on both modalities 
both_N_1 <- bimodal_bysub_1 %>%
  filter(abs(bimod) > 0.1) %>%
  filter(abs(bimod) < 10) %>%
  nrow()

#participants with noisy negative variances
neg_N_1 <- bimodal_bysub_1 %>%
  filter(bimod <  -0.1) %>%
  filter(bimod > -10) %>%
  nrow()

#Proportion of participants who relied only on the visual modality
exlusive_prop_1 = only_visual_N_1/(only_sound_N_1+only_visual_N_1)

```{r echo=FALSE, warning = FALSE}

#Simulated individual data from descriptive model model_fit0 without a bias term (equivalent to logitic regression)
#(but the values are very similar to descriptive model with bias the term model_fit1)

simulations <- data.frame()

#We aggregate simulted values for 50 times the number of participants  (in order to get a stable final distribution)
for (i in 1:50) {
Simul_exp1 <- joint_all_exp1 %>%
  select(ID, sound_dist, concept_dist) %>%
  mutate(prob = model_fit0(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer = rbinom(1, 1, prob=prob))

joint_bysub_sim_1 <- Simul_exp1 %>%
  group_by(ID) %>%
  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var) %>%
  select(ID, bimod) %>%
  filter(bimod > 0.1) %>%
  filter(bimod < 10)

  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
}

#Process and combine Real and Simulated data

  bimod_sim <- simulations  %>%
    mutate(data='simulation')

  bimod_real <- bimodal_bysub_good_1  %>%
    select(ID, bimod) %>%
    mutate(data='real')

  bimod_all <- bind_rows(bimod_real, bimod_sim)

#compare the sd of the distribtutions
 sd_ind<- bimod_all %>%
  group_by(data) %>%
  summarise(mean= mean(bimod),
            sd = sd(bimod))
```

```{r echo=FALSE, individual, out.width = "\\textwidth", fig.pos = "!h",fig.cap = "Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1. Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model."}

ggplot(data=bimod_all, aes(x=bimod, y=..ncount..)) +
  geom_histogram(data=subset(bimod_all, data=='real'), fill="red", alpha=0.2, binwidth = 0.2)+
  geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
  scale_x_log10() +
   xlab("Visual variance relative to sound variance") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7)

```
-->
